---
title: "Package swissvectormaps4r"
subtitle: "(Package Name under construction)"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## What is this package about?

I've developed this package to provide myself with a fast access to open vector data which I use frequently. I usually use this data to bring context to other data that I need to visualize. Check the reference section to see some metadata.

## How does this package work?

### Load the necessary packages

```{r,message=F}
# devtools::install_github("swissgeodata4r/swissvector4r")

library(swissvector4r) 

library(sf)
library(ggplot2)
library(dplyr)
```

### Plot the data
```{r}
data("kantonsgebiet")


ggplot(kantonsgebiet, aes(fill = Beitritt)) + 
  geom_sf() + 
  scale_fill_viridis_c() +
  coord_sf(datum = 2056)

```

```{r}
data("seen")
data("landesgebiet")

ggplot(landesgebiet) +
  geom_sf() +
  geom_sf(data = seen %>% arrange(desc(SHP_AREA)) %>% head(7), fill = "deepskyblue3")

```





## Who's in the team?

Currently, it's just [me](https://www.zhaw.ch/de/ueber-uns/person/rata/), but I'm very open to collaboration.

